Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-17 manuscripts/manuscript.Rmd
add cache rules on images

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')
```

@@

Figure 1 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs.

```{r Figure_1, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.  The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3}
ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("penalty coefficient") +
  ylab("Reduction in net present value")

@@

```{r Figure_2, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}

@@

<!-- NOTE 
Assuming we aren't showing cross-correlations, I think we can probably fit these into a single four subplot figure. Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.

Same comments as before on labeling the curves and detailing in the figure captions. Axis labels and things all also need work. - Paul
-->
<!--
Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB
-->

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}

@@

```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_wrap(~ timeseries + statistic, scale="free_y")

@@

```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8}

>>>>

library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

fig.cache <- TRUE
```

@@

Figure 2 shows the calibration graphically. Each curve plots the change
in maximum expected NPV for a given penalty function as the penalty cost
parameter is increased. In each case, the figure shows maximum expected
NPV with policy adjustment costs as a proportion of the maximum expected
NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy
adjustment costs.

```{r Figure_2, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost, $\\tfrac{NPV_0 - NPV_i}{NPV_0}$.  The horizontal line indicates a value of the stock that is reduced by `r reduction * 100`% from the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=4, fig.height=3, cache = fig.cache}
ggplot(fees, aes(c2, (npv0-value)/npv0, lty=variable)) + 
  geom_line() + 
  geom_hline(aes(yintercept=reduction), linetype=4) + 
  xlab("penalty coefficient") +
  ylab("Reduction in net present value")

@@

```{r Figure_3, dependson="tidy", fig.cap="Example realization of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs.", fig.height=3, fig.width=8, cache = fig.cache}

@@

<!--
Added cross-correlations but shows no pattern.  Also have version with 2x2 as single plot.  feedback on aesthetics welcome.  - CB

```{r Figure_4, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as well as cross-correlation between stock and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}

@@

-->

```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8, cache=fig.cache}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_wrap(~ timeseries + statistic, scale="free_y")

@@

```{r Figure_1S, dependson="tidy", fig.cap="Multiple realizations of optimal harvesting strategy and resulting fish stock sizes under the different functional forms of adjustment costs. Note that while fish stock dynamics appear similar in penalty and non-penalty scenarios, the harvest dyanmics show clear patterns depending on the type of penalty.", fig.height=3, fig.width=8, cache=fig.cache}
